Traffic aware Resource Allocation for \acs{MIMO}-\acs{OFDM} systems

### 2014-09-12 Report/wsrm_formulation.tex
updated version

In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers obtained
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, the linear approximation is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\partial f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \partial \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
\end{subeqnarray}
where \me{\bar{f}(x,x^{(i)})} is the approximate function \me{\bar{f}(x)} around the point \me{x^{(i-1)}}. At each iteration \me{(i-1)}, the optimal value \me{x^{\ast}} obtained by solving the approximate problem is a feasible solution to next approximation at \me{(i)} iteration by following \eqref{sca-req}. It can be easily verified that the optimal point of each \ac{SCA} problem satisfies the \ac{KKT} condition of the original problem, which in fact is the stationary point of the \ac{SCA} subproblem.

The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders. The monotonic convergence of the objective function can be justified by the following arguments. At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function. Since the \ac{SCA} subproblem is relaxed around the \me{\ith{(i-1)}} optimal point for the \me{\ith{(i)}} iteration, the solution of the \me{\ith{(i)}} iteration includes optimal point from the  \me{\ith{(i-1)}} iteration as well. Therefore, at each \ac{SCA} iteration, the objective function can either be equal to or smaller than the previous solution, thereby leading to the monotonic convergence of the objective function.

Once the problem converged to an optimal point, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}. Since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.

>>>>

In order to prove the convergence of the proposed algorithm, we require the following conditions to be satisfied
\begin{itemize}
	\item convergence of the \ac{SCA} subproblem	
	\item uniqueness of the transmit and the receive beamformers obtained
	\item monotonic convergence of the objective function
\end{itemize}
In the proposed solution, we replaced \eqref{eqn-6.2} by a convex constraint using the first order approximation, which is majorized by the quadratic-over-linear function in \eqref{eqn-6.2} from below around a fixed point \me{\tilde{\mbf{u}}^{(i)}_{l,k,n}}. Since the \ac{SCA} method is adopted in the proposed algorithm, the constraint approximation satisfies the following conditions as in \cite{marks1978technical}
\begin{subeqnarray} \label{sca-req}
	f(\tilde{\mbf{u}}_{l,k,n}) &\leq& \bar{f}(\tilde{\mbf{u}}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n}) \\
	\nabla f(\tilde{\mbf{u}}^{(i)}_{l,k,n}) &=& \nabla \bar{f}(\tilde{\mbf{u}}^{(i)}_{l,k,n},\tilde{\mbf{u}}^{(i)}_{l,k,n})
\end{subeqnarray}
where \me{\bar{f}(x,x^{(i)})} is the approximate function of \me{f(x)} around the point \me{x^{(i)}}. Using the assumptions in \eqref{sca-req}, the global optimal point of the relaxed formulation, which is a convex problem, satisfies the \ac{KKT} conditions of the original nonconvex problem, using \eqref{sca-req}. It shows that each relaxed formulation converges to the optimal point.

The uniqueness of the transmit and the receive beamformers can be justified by forcing one antenna to be real valued to exclude the phase ambiguity arising from the complex precoders. The monotonic convergence of the objective function can be justified by the following arguments. At each \ac{SCA} iteration, the relaxed subproblem is solved for the optimal transmit precoders to minimize the objective function. Since the \ac{SCA} subproblem is relaxed around the \me{\ith{i-1}} optimal point,\textit{i.e} \me{x^{\ast(i-1)}}, for the \me{\ith{i}} iteration, the domain of the problem in the \me{\ith{i}} step includes optimal point from the  \me{\ith{i-1}} iteration as well. Therefore, at each \ac{SCA} steps, the objective function can either be equal to or smaller than the previous value, thereby leading to the monotonic convergence of the objective function.

Once the problem converged to an optimal transmit precoders, the receive beamformers are updated based on the receivers mentioned in \eqref{opt-rx} or \eqref{eqn-10}. The monotonic nature of the objective function is preserved by the receive beamformer update, since the receiver minimizes the objective value for the fixed transmit precoders, the proposed \ac{JSFRA} scheme guarantees to converge to an optimal point.
